The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-18 paper/authors.tex
affils
authors
FFNN fixes
add orcid
more authors and notes

@@

\author{Eduardo S. Cypriano} $^3$
\affiliation{Universidade de S\~ao Paulo, IAG, Rua do Mat\~ao 1225, S\~ao Paulo, SP, Brazil}

@@

\author[0000-0002-0226-9893]{Elizabeth J. Gonzalez} $^{4,5}$.
\affiliation{Instituto de Astronom\'{\i}a Te\'orica y Experimental (IATE-CONICET), Laprida 854, X5000BGR, C\'ordoba, Argentina.}

@@

\author{Peter Hatfield}
\noaffiliation

\author{Kartheik Iyer}
\noaffiliation

@@

\author{Alex Malz}
\noaffiliation

@@

\author{Erfan Nourbakhsh}
\noaffiliation

@@

\author{Angus Wright}
\noaffiliation

>>>>

\author[0000-0001-7363-7932]{Angus Wright}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

@@

\author{Eduardo S. Cypriano}
\affiliation{Universidade de S\~ao Paulo, IAG, Rua do Mat\~ao 1225, S\~ao Paulo, SP, Brazil}

@@

\author[0000-0002-0226-9893]{Elizabeth J. Gonzalez}
\affiliation{Instituto de Astronom\'{\i}a Te\'orica y Experimental (IATE-CONICET), Laprida 854, X5000BGR, C\'ordoba, Argentina.}

@@

\author[0000-0002-3065-457X]{Peter Hatfield}
\affiliation{Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}

\author[0000-0001-9298-3523]{Kartheik Iyer}
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St George St, Toronto, ON M5S 3H4, Canada}

@@

\author{Alex Malz}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

@@

\author[0000-0003-3827-4691]{Erfan Nourbakhsh}
\affiliation{Department of Physics and Astronomy, University of California, Davis, Davis, CA 95616, USA}

@@
